Detecting Hand Direction for Computer Interaction

### 2014-12-10 paper/paper.tex

\subsection{Regression}
We experimented with several different including k-Nearest Neighbors and linear regression. We found that a combination of k-nearest neighbors worked best across a wide variety of data. We trained the k-nearest neighbors and linear regression models from sci-kit learn separately on 15 sets of test data comprised of the HOG features computed from each image. These models each predicted a location based on HOG input. These locations were averaged together and fed into a smoothing algorithm to compute the final location.

>>>>

\subsection{Regression}
We experimented with several different regression models including k-Nearest Neighbors, and least squares linear regression. We found that an average of the output of k-nearest neighbors and linear regression worked best across a wide variety of data. We trained the k-nearest neighbors and linear regression models using the scikit-learn library\cite{scikit-learn}.  The models took in the features vectors from HOG and the neural networks and predicted a location. These locations were averaged together and fed into a smoothing algorithm to compute the final location.
